\itTopic{en}{uk}{lash}{prayersvarious}
\itKey{ltType}{
resource
}%
\itKey{ltTopic}{
prayersvarious
}%
\itKey{ltDomain}{
en_uk_lash
}%
\itKey{p0001}{
duplicates.d1212
}%
\itKey{p0002}{
duplicates.d0754
}%
\itKey{p0003}{
BLESSING OF ANIMALS (ST. MODESTOS)
}%
\itKey{p0004}{
O Lord Jesus Christ our God, compassionate and all-good, who fashioned in wisdom both the invisible and the visible creation; who pour your mercies upon everything that has been made by you; who,in your loving providence, provide for all your creatures, from the first to the last; hear my prayer and drive away and banish every injury and illness from all these cattle (or sheep, or horses or other animals) which are being used for the livelihood of your servant(s)(N). Yes, Lord, look down from your holy dwelling place and bless all these animals, as you blessed the ﬂocks of Abraham, Isaac and Jacob, and of all your faithful servants. Multiply them, grant them health, strength and productivity; render them robust and successful in the various services which they render. So that their owners, having derived abundant benefits from them, may engage in all good works which are pleasing to you, and my glorify on earth your holy name, of the Father and of the Son and of the Holy Spirit. Amen.
}%
\itKey{p0005}{
PRAYER AGAINST BAD WEATHER
}%
\itKey{p0006}{
O Master, Lord our God, who through your consubstantial and beginningless Word, and your life-giving Spirit who is equal in honor, have brought verything out of nothingness into being; who have set sandy barriers to the sea, and weighed the mountains and the valleys in a balance; who have measured the skies and hold the water in the palm of your hand; who have given to this visible world of the senses its laws and rules, its harmony and order; who have appointed changes to the weather and variations in the orbit of the sun; who, through the mingling of the elements, hold all things together by your inexpressible power, and keep them free from harm and intact: Do you yourself, all-good King, extending to us your innate and customary love and goodness, visit the works of your hands. Do not deprive us of your mercies and your compassion, and do not destroy your inheritance, for you have ineffably created us in your own image. You have given your only-begotten Son as a ransom for us, and through the mystical comunion of your Spirit have made us share in your own divinity; forgive, we pray, the multitude of our sins in the far greater multitude, of your mercies. You washed away the sin of mankind through the Cross and the Blood of your Son. Restore the world of nature, which has been grievously disturbed into an unnatural state because of the unruliness and disorderliness of our lawless and corrupt behavior, and bring it back to its natural harmony and order. Make the great ocean return to its usual calmness, bring to end the tempest and the disturbance of the elements that threatens us, order the winds to blow once more with gentleness and moderation. Rebuke the raging of the sea and the unnatural violence of the gales; let the spirit of the storm be stilled and the tempest return to tranquility.
}%
\itKey{p0007}{
Through the intercessions of the most blessed Lady Theotokos, of the God-like Angels and all the Saints, and through the good pleasure and love of your only-begotten Son with whom you are blessed, together with your all-holy and good and life- giving Spirit, now and ever, and to the ages of ages. Amen.
}%
\itKey{p0008}{
duplicates.d0174
}%
\itKey{p0009}{
Lord Jesus Christ our God, wonderful in your saints, who hear our intercessions and fulfill our requests that are for our good, bless this loaf which has been prepared by your servant N. (your servants N.N.) and is now offered in thanksgiving and glorification for what they have enjoyed from you through the intercession of the holy and glorious newly revealed Martyr and wonderworker Phanourios, and in memory of those who have died in the faith. Give them rest in your Kingdom and preserve us all in health as we do your will in peace and offer you thanks for all your gifts. Make our life peaceful, grant us those requests that are for our salvation, bestowing on us your earthly and heavenly blessings, at the intercessions of our most holy lady, the Mother of God, of the holy, glorious Martyr Phanourios and of all your saints.
}%
\itKey{p0010}{
duplicates.d0340
}%
\itKey{p0011}{
PRAYER ON THE FIRST DAY OF THE YEAR
}%
\itKey{p0012}{
O Lord our God, who have placed times and seasons under your own authority; who, in your infinite compassion and goodness, have counted us worthy to enter a New Year of your loving kindness, bless it and keep us in peace. Loose, remit and forgive any sins that we have committed during the year that is past, and keep us free from sin in the new year. Enlighten us with the light of your truth and your divine commandments. Establish in our souls your holy will, and guide us to every work that is good and pleasing to you. Guard well our holy Church with your divine grace. Remember, Lord, our nation; train up the youth; protect the elderly; encourage the faint-hearted; gather the scattered; bring back those who have gone astray, and reunite them to your holy Church. Overshadow our Land with your might, and grant it gentle rain and abundance of the fruits of the earth. Speak of goodness in the hearts of our rulers; support and strengthen them, together with our armed forces by land, sea and air so that in their tranquility we may lead our life in every piety and dignity. Let your kingdom come upon us, O Lord; the kingdom of love, goodness, peace and justice; and make us worthy to praise and glorify, with one mouth and one heart, your most honorable and majestic name, of the Father and of the Son and of the Holy Spirit, now and ever, and to the ages of ages. Amen.
}%
\itKey{p0013}{
duplicates.d0743
}%
\itKey{p0014}{
Lord Jesus Christ, Son of the living God, Shepherd and Lamb, who takes way the sin of the world, you forgave the two debtors their loan and granted the sinful woman forgiveness of her sins. Remit, forgive, pardon, Master, the sins, iniquities, and offences, voluntary or involuntary, committed by these servants of yours, both knowingly and unwittingly, through transgression and disobedience. And if, as human beings clothed in flesh and living in the world, they have in any way been led astray by the Devil, whether in word or deed, knowingly or unwittingly; if they have trampled on the word of a priest, or come under the curse of a priest; if they have fallen under their own anathema, or been made subject to an oath, as you are good, Master, and do not remember evils, be well pleased for these servants of yours to be loosed by a word, in accordance with your great mercy granting them absolution from their own anathema and oath. Master and Lord who loves mankind, hear us therefore as we implore your goodness on behalf of these servants of yours, and, as you are full of mercy, overlook all their faults. Deliver them from eternal punishment. For you said, Master, ‘Whatever you bind on earth will be bound in heaven, and whatever you loose on earth will be loosed in heaven’. For you alone are without sin, and to you we give glory, together with your Father who is without beginning, and your all-holy, good, and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itKey{p0015}{
duplicates.d0175
}%
\itKey{p0016}{
On Palm Sunday
}%
\itKey{p0017}{
Lord, our God, who are seated upon the Cherubim, you roused your power and sent your only-begotten Son, our Lord Jesus Christ, to save the world through his Cross, Burial and Resurrection. As he drew near to Jerusalem for his voluntary Passion, the people that sat in darkness and the shadow of death, taking the symbols of victory, boughs of trees and branches of palms, foreshadowed his Resurrection. Keep us yourself, Master, and preserve us, who, following their example, on this day before the Feast carry palms and branches in our hands and, like those crowds and those children, offer you our ‘Hosanna!’, so that with hymns and spiritual songs we may be counted worthy of the life-giving Resurrection on the third day; in Christ Jesus, our Lord, with whom you are blessed, together with your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itKey{p0018}{
duplicates.d0100
}%
\itKey{p0019}{
BLESSING OF VEHICLE
}%
\itKey{p0020}{
Lord Jesus Christ our God, who came to earth to save mankind; who move about in heaven borne on a throne; who on earth went round the cities and towns on foot; who, shortly before your voluntary Passion, entered the Holy City, sitting on the colt of a donkey; who through your Angel spoke to Philip (the Apostle) and told him to rise and go toward the south to the road that goes down from Jerusalem to Gaza and join the chariot of the Ethiopian whom, after evangelizing, he baptized: Do you yourself, O Master, bless this vehicle (and the Priest sprinkles the vehicle with holy water) and grant that your servant(s) (N) may use it with joy and finish the course and the service which he (she) (they) was (were) given by you. Give him (her) (them) the wisdom to use all avenues of progress with prudence, love and consideration for his (her) (their) neighbor, so that they may become for him (her) (them) highways of growth in your direction instead of pathways to his (her) (their) extinction. For to finish the course does not lie in the power of the one who chooses or the one who runs, but in your power, O merciful God; therefore, we pray to you to give us a shining Angel to go before us an deliver us from all evil by night and day; so that led by the Spirit of God we may journey well and not labor in vain. ‘For you are the way, the truth and the life, and to you we ascribe glory and thanksgiving, together with your beginningless Father and your all-holy and good and life-giving Spirit, now and ever, and to the ages of ages. Amen.
}%
\itKey{p0021}{
duplicates.d0743
}%
\itKey{p0022}{
Lord Jesus Christ, Son of the living God, Shepherd and Lamb, who takes away the sin of the world, you forgave the two debtors their loan and granted the sinful woman forgiveness of her sins. Remit, forgive, pardon, Master, the sins, iniquities, and offences, voluntary or involuntary, committed by these servants of yours, both knowingly and unwittingly, through transgression and disobedience. And if, as human beings clothed in flesh and living in the world, they have in any way been led astray by the Devil, whether in word or deed, knowingly or unwittingly; if they have trampled on the word of a priest, or come under the curse of a priest; if they have fallen under their own anathema, or been made subject to an oath, as you are good, Master, and do not remember evils, be well pleased for these servants of yours to be loosed by a word, in accordance with your great mercy granting them absolution from their own anathema and oath. Master and Lord who loves mankind, hear us therefore as we implore your goodness on behalf of these servants of yours, and, as you are full of mercy, overlook all their faults. Deliver them from eternal punishment. For you said, Master, ‘Whatever you bind on earth will be bound in heaven, and whatever you loose on earth will be loosed in heaven’. For you alone are without sin, and to you we give glory, together with your Father who is without beginning, and your all-holy, good, and life-giving Spirit, now and for ever, and to the ages of ages.BLESSING EGGS
}%
\itKey{p0023}{
duplicates.d0280
}%
\itKey{p0024}{
duplicates.d0497
}%
\itKey{p0025}{
duplicates.d0653
}%
\itKey{p0026}{
duplicates.d0296
}%
