\itTopic{en}{uk}{lash}{ps.kenya.alt}
\itKey{psa17.v2alt.text}{
I will love You, Lord, my strength.
}%
\itKey{psa50alt.text}{
Have mercy on me, O God, according to Your great mercy; and according to the abundance of Your compassion, blot out my transgression. Wash me thoroughly from my lawlessness and cleanse me from my sin. For I know my lawlessness, and my sin is always before me. Against You only have I sinned and done evil in Your sight; that You may be justified in Your words, and overcome when You are judged. For behold, I was conceived in transgressions, and in sins my mother bore me. Behold, You love truth; You showed me the unknown and secret things of Your wisdom. You shall sprinkle me with hyssop, and I will be cleansed; You shall wash me, and I will be made whiter than snow. You shall make me hear joy and gladness; my bones that were humbled shall greatly rejoice. Turn Your face from my sins, and blot out all my transgressions. Create in me a clean heart, O God, and renew a right spirit within me. Do not cast me away from Your presence, and do not take Your Holy Spirit from me. Restore to me the joy of Your salvation, and uphold me with Your guiding Spirit. I will teach transgressors Your ways, and the ungodly shall turn back to You. Deliver me from bloodguiltiness, O God, the God of my salvation, and my tongue shall greatly rejoice in Your righteousness. O Lord, You shall open my lips, and my mouth will declare Your praise. For if You desired sacrifice, I would give it; You will not be pleased with whole burnt offerings. A sacrifice to God is a broken spirit, a broken and humbled heart God will not despise. Do good, O Lord, in Your good pleasure to Zion, and let the walls of Jerusalem be built; then you will be pleased with a sacrifice of righteousness, with offerings and whole burnt offerings; then shall they offer young bulls on Your altar.
}%
\itKey{psa133.v2alt2.text}{
Lift up your hands to the holy place and bless the Lord.
}%
\itKey{psa118.v12alt.text}{
Blessed are You, O Lord; Teach me Your statutes.
}%