\itTopic{en}{uk}{lash}{ps}
\itKey{psa148.v1.text}{
Praise the Lord from heaven, praise him in the highest.
}%
\itKey{psa25.v11.text}{
But I have walked in my innocence; rescue me, Lord, and have mercy on me.
}%
\itKey{psa44.v10b.text}{
The Queen stood at your right hand, clothed in a garment woven with gold, and of many colours.
}%
\itKey{psa32.v6.text}{
By the Word of the Lord the heavens were made firm, and by the Spirit of his mouth all their power.
}%
\itKey{psa145.v1.number}{
(145:1)
}%
\itKey{psa118.v73.text}{
Your hands have made me and fashioned me; give me understanding and I will learn your commandments.
}%
\itKey{psa145.v6.number}{
(145:6)
}%
\itKey{psa35.v10.text}{
For with you is the source of life, * and in your light we shall see light.
}%
\itKey{psa40.v5.text}{
I said, * Lord, have mercy on me, * heal my soul, * for I have sinned against you.
}%
\itKey{psa117.v24.number}{
(117:24)
}%
\itKey{psa35.v11a.text}{
Continue your mercy * towards those who know you.
}%
\itKey{psa17.v33.text}{
who girds me with power and has made my way blameless.
}%
\itKey{psa25.v8.text}{
Lord, I have loved the beauty of your house, and the place of the dwelling of your glory.
}%
\itKey{psa102.v22.text}{
Bless the Lord, all his works, in every place of his dominion; bless the Lord, O my soul!
}%
\itKey{psa117.v1.text}{
Give thanks to the Lord, for he is good, for his mercy endures for ever.
}%
\itKey{psa145.v2.text}{
while I live I will praise the Lord; while I exist, I will praise my God.
}%
\itKey{psa102.v19.text}{
The Lord has prepared his throne in heaven, and his kingdom rules over all.
}%
\itKey{psa145.v6.text}{
Who made heaven and earth, the sea and all that is in them.
}%
\itKey{psa117.v4.number}{
(117:4)
}%
\itKey{psa117.v24.text}{
This is the day which the Lord has made; let us rejoice and be glad in it.
}%
\itKey{psa132.v2.text}{
as myrrh upon the head, which ran down upon the beard, Aaron’s beard, and ran down to the collar of his robe.
}%
\itKey{psa50.v20.text}{
Do good to Sion, Lord, in your good pleasure, and let the walls of Jerusalem be rebuilt.
}%
\itKey{psa50.v17.text}{
Lord, you will open my lips, and my mouth will proclaim your praise.
}%
\itKey{psa32.v22.text}{
May your mercy, O Lord, * be upon us, * as we have hoped in you.
}%
\itKey{psa25.v12.text}{
My foot has stood in the right path; in the churches I will bless you, O Lord.
}%
\itKey{psa50.v21b.text}{
Then they will offer calves upon your altar.
}%
\itKey{psa25.v9.text}{
Do not destroy my soul with the ungodly, nor my life with men of blood.
}%
\itKey{psa102.v19.number}{
(102:19)
}%
\itKey{psa145.v10.number}{
(145:10)
}%
\itKey{psa102.v1.number}{
(102:1)
}%
\itKey{psa117.v26a.text}{
Blessed is he who comes in the name of the Lord.
}%
\itKey{psa144.v2.text}{
Every day I will bless you, * and praise your name for ever * and to the ages of ages.
}%
\itKey{psa145.v5.number}{
(145:5)
}%
\itKey{psa102.v1.text}{
Bless the Lord, O my soul, and all that is within me, bless his holy name.
}%
\itKey{psa44.v5.text}{
and bend the bow, prosper and reign, for the sake of truth and meekness and justice, and your right hand will guide you wondrously.
}%
\itKey{psa117.v4.text}{
Let all those who fear the Lord say that he is good, that his mercy endures for ever.
}%
\itKey{psa92.v1c.text}{
the Lord has clothed and girded himself with power.
}%
\itKey{psa142.v10alt.text}{
Lord, I have run to you for refuge, * teach me to do your will, * for you are my God.
}%
\itKey{psa145.v5.text}{
Blessed are those whose helper is the God of Jacob; whose hope is in the Lord their God.
}%
\itKey{psa25.v6.text}{
I will wash my hands among the innocent, and I will go around your altar, Lord;
}%
\itKey{psa102.v2.text}{
Bless the Lord, O my soul, and forget none of his rewards.
}%
\itKey{psa102.v22.number}{
(102:22)
}%
\itKey{psa33.v11.text}{
The rich have become poor and hungry, while those who seek the Lord will not lack any good thing.
}%
\itKey{psa50.v21a.text}{
Then you will be well pleased with a sacrifice of righteousness, oblation and whole burnt offerings.
}%
\itKey{psa112.v2alt1.text}{
Blessed be the name of Lord, from this time forth and for evermore.
}%
\itKey{psa5.v8.text}{
I will enter your holy house; I will bow down before your holy temple in fear of you.
}%
\itKey{psa92.v1b.text}{
The Lord is King, he has clothed himself with majesty;
}%
\itKey{psa131.v9alt.text}{
Your priests, Lord, will clothe themselves with righteousness, and your holy ones will rejoice with gladness.
}%
\itKey{psa25.v10.text}{
In whose hands are iniquities; their right hand is filled with bribes.
}%
\itKey{psa67.v27.text}{
Bless God in the Churches; the Lord from the fountains of Israel.
}%
\itKey{psa89.v1.text}{
Lord, * you have been our refuge * from generation to generation.
}%
\itKey{psa56.v6.text}{
Be exalted, O God, above the heavens; and your glory over all the earth.
}%
\itKey{psa102.v2.number}{
(102:2)
}%
\itKey{psa117.v1.number}{
(117:1)
}%
\itKey{psa25.v7.text}{
to hear the voice of your praise and tell of all your wonderful works.
}%
\itKey{psa145.v10.text}{
The Lord will be king for ever: your God, O Sion, will reign throughout all generations.
}%
\itKey{psa44.v4.text}{
Gird your sword on your thigh, O Powerful One, in your beauty and splendour;
}%
\itKey{psa145.v1.text}{
Praise the Lord, O my soul:
}%
\itKey{psa17.v2.text}{
I will love you, Lord, my strength.
}%
\itKey{psa17.v3a.text}{
The Lord is my firm foundation, my refuge and my deliverer.
}%
