\itTopic{en}{uk}{lash}{ho.s03}
\itKey{hoMA.DoxologyVerse06.text}{
For you alone are holy, * you alone are Lord, * Jesus Christ, * to the glory of God the Father. Amen.
}%
\itKey{hoMA.FuneralEvlog8.text}{
Hail, honoured one, who bore God in the flesh for the salvation of all; through you the human race has found salvation; through you may we find Paradise, O pure and blessed Mother of God.
}%
\itKey{hoMA.FuneralEvlog4.text}{
I am an image of your ineffable glory, though I bear the marks of offences; take pity on your creature, Master, and with compassion cleanse me; and give me the longed-for fatherland, making me once again a citizen of Paradise.
}%
\itKey{hoMA.DoxologyVerse04.text}{
Lord God, * Lamb of God, * Son of the Father, * who takes away the sin of the world, * have mercy on us; * you take away the sins of the world.
}%
\itKey{hoMA.SunTroparion2.text}{
By rising from the tomb * and bursting through the bonds of Hades, * you abolished the sentence of death, O Lord, * delivering all from the snares of the foe. * Having shown yourself to your Apostles, * you sent them out to preach, * and through them you gave peace * to the inhabited world, * you who alone are full of mercy.
}%
\itKey{hoMA.FuneralEvlog1.text}{
The choir of Saints has found the source of life and the door of Paradise; may I too find the way through repentance; I am the lost sheep, call me back, O Saviour, and save me.
}%
\itKey{hoMA.DoxologyVerse05.text}{
Receive our prayer, * you who sit at the right hand of the Father, * and have mercy on us.
}%
\itKey{hoMA.FuneralEvlog7.text}{
Let us devoutly hymn the threefold light of the one Godhead as we cry: Holy are you, the Father without beginning, the Son likewise without beginning and the divine Spirit; enlighten us who worship you in faith, and snatch us from the everlasting fire.
}%
\itKey{hoMA.SunPostGospel.text}{
Having seen the Resurrection of Christ...,
}%
\itKey{hoMA.DoxologyVerse08.text}{
Grant, Lord, * this day * to keep us without sin.
}%
\itKey{hoMA.DoxologyGreat.title}{
THE GREAT DOXOLOGY
}%
\itKey{hoMA.FuneralEvlog6.text}{
Give rest, O God, to your servant(s), and settle him (her/them) in Paradise, where the choirs of the Saints and all the Just shine out like beacons; give rest to your servant(s) who has (have) fallen asleep, overlooking all his (her/their) offences.
}%
\itKey{hoMA.FuneralEvlog5.text}{
Of old you formed me from nothing and honoured me with your divine image, but because I transgressed your commandment, you returned me to the earth from which I was taken; bring me back to your likeness, my ancient beauty.
}%
\itKey{hoMA.DoxologyVerse19.text}{
Holy Immortal, have mercy on us.
}%
\itKey{hoMA.DoxologyGreatIntro.text}{
Glory to you who have shown us the light.
}%
\itKey{hoMA.DoxologyVerse02.text}{
We praise you, * we bless you, * we worship you, * we glorify you, * we give you thanks * for your great glory.
}%
\itKey{hoMA.SunTroparion1.text}{
Today salvation has come to the world. * Let us sing to him who rose from the tomb, the Author of our life. * For destroying death by death, * he has given us the victory * and his great mercy.
}%
\itKey{hoMA.DoxologyVerse03.text}{
Lord, King, * God of heaven, * Father, Almighty, * Lord, only-begotten Son, * Jesus Christ * and holy Spirit.
}%
\itKey{hoMA.SunPostGospel.text}{
\color{black}\itRid{ho.s03}{hoMA.SunPostGospel.text.a}\color{red}
}%
\itKey{hoMA.SunPostGospel.text.a}{
Having seen the Resurrection of Christ...,
}%