\itId{sqi}{alb}{koas}{copyright}{notice}{
TBD
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgy.title.cover}{
MESHA HYJNORE E ATIT TONË NDËR SHENJTORËT, JOAN GOJARTIT
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgy.title.toc}{
MESHA HYJNORE E ATIT TONË NDËR SHENJTORËT, JOAN GOJARTIT
}%
\itId{sqi}{alb}{koas}{client}{li.hierarchical.sponsor.title.cover}{
Kisha Orthodhokse Autoqefale e Shqipërisë
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgycatechumens.title.doc}{
The Liturgy of the Catechumens
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.liturgy.deacon.start}{
The Deacon, having received a blessing from the Priest, comes out of the Sanctuary by the North Door and, standing in his usual place in front of the Holy Doors, makes three bows and begins:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.bless}{
Beko, o Zot.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.beginliturgy}{
The Priest, lifting up the book of the Gospel, and making the sign of the Cross with it over the Antimension, says in a clear voice:
}%
\itId{sqi}{alb}{koas}{prayers}{enarxis02}{
E bekuar është mbretëria e Atit, e Birit dhe e Shpirtit të Shenjtë, tani e përherë e në jetë të jetëve.
}%
\itId{sqi}{alb}{koas}{actors}{People}{
Psaltët
}%
\itId{sqi}{alb}{koas}{prayers}{res04}{
Amin.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.litanypeace.title.doc}{
Litany of Peace
}%
\itId{sqi}{alb}{koas}{actors}{Deacon}{
Dhiaku
}%
\itId{sqi}{alb}{koas}{prayers}{pet01}{
Me paqe le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{res01}{
Mëshiro, o Zot.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.eachpetition}{
And so after each petition.
}%
\itId{sqi}{alb}{koas}{prayers}{pet02}{
Për paqen që lartazi, dhe për shpëtimin e shpirtrave tanë, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{pet03}{
Për paqen e tërë botës, qëndrimin e mirë të Kishave të shenjta të Perëndisë, dhe për bashkimin e të gjithëve, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{pet04}{
Per këtë shtëpi te shenjtë dhe për ata që hyjnë brenda në të me besë, shpresëtari dhe frikë Perëndie, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{pet06}{
Për Kryepiskopin tonë \textunderscore\textunderscore\textunderscore\textunderscore, episkopin (t) \textunderscore\textunderscore\textunderscore\textunderscore, të nderuarën presviteri dhe dhiakonatën më Krishtin, per tërë klerin dhe popullin, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{pet07S}{
Për Republikën e Shqipërisë, Qeverinë, Ushtrinë dhe gjithë popullin, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{pet08}{
Për këtë qytet (ose manastir të shenjtë), çdo qytet dhe vend dhe për ata që banojnë në to me besë, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{pet09}{
Për erëra të mira, begati të pemëve të dheut, dhe për kohë me paqe, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{pet10}{
Për ata që lundrojnë, qe udhëtojnë, për të sëmurët, vuajtësit, robërit dhe për shpëtimin e tyre, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{pet11}{
Që të shpëtojmë prej çdo hidhërimi, zemërimi, rreziku dhe nevoje, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{prayers}{pet12}{
Përkrahna, shpëtona, mëshirona dhe ruajna, o Perëndi me hirin tënd.
}%
\itId{sqi}{alb}{koas}{prayers}{pet13}{
Të Tërëshënjtën, të pacënuarën, të përmbibekuarën, të lavdëruarën Zonjën tonë Hyjlindëse dhe gjithmonë Virgjërën Mari, bashkë me gjithë shenjtorët, duke e kujtuar, veten tonë dhe njëri--tjetrin dhe gjithë jetën tonë, Krishtit Perëndisë, le t'i a parashtrojmë.
}%
\itId{sqi}{alb}{koas}{prayers}{res03}{
Ty, o Zot.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerantifon1.title.doc}{
Urata e Andifonit të parë
}%
\itId{sqi}{alb}{koas}{actors}{InALowVoice}{
(pa zë)
}%
\itId{sqi}{alb}{koas}{actors}{Priest}{
Prifti
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0201.text}{
0 Zot, Perendia yne, shpeto popullin tend dhe beko trashegimin tend; tere benimtaret e Kishes sate ruaji; shenjteroi ata qe duan hijeshine e shtepise sate. Edhe Ti Iavderoi ata me fuqine tende te perendishme dhe mos na Ier ne qe shpresojme tek Ti.
}%
\itId{sqi}{alb}{koas}{actors}{Aloud}{
(më zë të lartë)
}%
\itId{sqi}{alb}{koas}{prayers}{exc01}{
Se Ty të përket tërë lavdia, nderimi dhe adhurimi, Atit e Birit edhe Shpirtit të Shenjtë, tani e përherë e në jetë të jetëve.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.antifon1.title.doc}{
First Antiphon
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.iffeast}{
If it is a feast of the Lord, or of the Mother of God, or its afterfeast or leavetaking, the Antiphons of the feast are sung; otherwise the Typika are used.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.sundayantifon1}{
On Sundays the following Antiphon is usually sung:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.verseantifon1}{
Mode 2. Psalm 102
}%
\itId{sqi}{alb}{koas}{misc}{vVerse1}{
1st Verse:
}%
\itId{sqi}{alb}{koas}{ps}{psa102.v1.text}{
Bless the Lord, O my soul, and all that is within me, bless his holy name.
}%
\itId{sqi}{alb}{koas}{ps}{psa102.v1.number}{
(102:1)
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.Antiphon1.text}{
Me ndërmjetimet e Hyjlindëses, Shpëtimtar shpëtona.
}%
\itId{sqi}{alb}{koas}{misc}{vVerse2}{
2nd Verse:
}%
\itId{sqi}{alb}{koas}{ps}{psa102.v2.text}{
Bless the Lord, O my soul, and forget none of his rewards.
}%
\itId{sqi}{alb}{koas}{ps}{psa102.v2.number}{
(102:2)
}%
\itId{sqi}{alb}{koas}{misc}{vVerse3}{
3rd Verse:
}%
\itId{sqi}{alb}{koas}{ps}{psa102.v19.text}{
The Lord has prepared his throne in heaven, and his kingdom rules over all.
}%
\itId{sqi}{alb}{koas}{ps}{psa102.v19.number}{
(102:19)
}%
\itId{sqi}{alb}{koas}{misc}{vVerse4}{
4th Verse:
}%
\itId{sqi}{alb}{koas}{ps}{psa102.v22.text}{
Bless the Lord, all his works, in every place of his dominion; bless the Lord, O my soul!
}%
\itId{sqi}{alb}{koas}{ps}{psa102.v22.number}{
(102:22)
}%
\itId{sqi}{alb}{koas}{prayers}{DoxaPatri.text}{
Glory to the Father, and to the Son, and to the Holy Spirit.
}%
\itId{sqi}{alb}{koas}{prayers}{KaiNynKaiAei.text}{
Both now and for ever, and to the ages of ages. Amen.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconpositionantifon1}{
While this is being sung the Deacon bows, leaves his place and goes and stands in front of the icon of the Mother of God, looking towards the icon of Christ, holding his orarion in the three fingers of his right hand.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconlitany}{
After the completion of the Antiphon he comes and stands in his usual place, bows and says the Short Litany.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.smalllitany.title.doc}{
Short Litany
}%
\itId{sqi}{alb}{koas}{prayers}{pet14}{
Përsëri dhe përsëri me paqe, le t'i lutemi Zotit.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerantifon2.title.doc}{
Prayer of the Second Antiphon
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0301.text}{
0 Zot, Perëndia ynë, shpëto popullin tënd dhe beko trashëgimin tënd; tërë benimtarët e Kishës sate ruaji; shenjtëroi ata që duan hijeshinë e shtepisë sate. Edhe Ti lavdëroi ata me fuqinë tendë te perëndishme dhe mos na ler ne që shpresojmë tek Ti.
}%
\itId{sqi}{alb}{koas}{prayers}{exc02}{
Se yti është pushteti dhe jotja  është mbretëria, dhe fuqia, dhe Iavdia, e Atit, e Birit dhe e Shpirtit të Shenjtë, tani e përherë e në jetë të jetëve.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.antifon2.title.doc}{
Second Antiphon
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.sundayantifon2}{
The second Psalm of the Typika or, on Sundays, the following Antiphon:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.verseantifon2}{
Mode 2. Psalm 145
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.notsunday}{
On weekdays, outside Eastertide, or a feast of the Lord, we sing after each verse:
}%
\itId{sqi}{alb}{koas}{me.m10.d28}{alt1.meLI.Antiphon2.text}{
Son of God, wonderful in the Saints, save us who sing to you: Alleluia!
}%
\itId{sqi}{alb}{koas}{ps}{psa145.v1.text}{
Praise the Lord, O my soul:
}%
\itId{sqi}{alb}{koas}{ps}{psa145.v2.text}{
while I live I will praise the Lord; while I exist, I will praise my God.
}%
\itId{sqi}{alb}{koas}{ps}{psa145.v1.number}{
(145:1)
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.Antiphon21.text}{
Son of God,
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.Antiphon2s.text}{
risen from the dead,
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.Antiphon22.text}{
save us who sing to you: Alleluia!
}%
\itId{sqi}{alb}{koas}{ps}{psa145.v5.text}{
Blessed are those whose helper is the God of Jacob; whose hope is in the Lord their God.
}%
\itId{sqi}{alb}{koas}{ps}{psa145.v5.number}{
(145:5)
}%
\itId{sqi}{alb}{koas}{ps}{psa145.v6.text}{
Who made heaven and earth, the sea and all that is in them.
}%
\itId{sqi}{alb}{koas}{ps}{psa145.v6.number}{
(145:6)
}%
\itId{sqi}{alb}{koas}{ps}{psa145.v10.text}{
The Lord will be king for ever: your God, O Sion, will reign throughout all generations.
}%
\itId{sqi}{alb}{koas}{ps}{psa145.v10.number}{
(145:10)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.alldays}{
Then, on all days:
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.OnlyBegotten.text}{
O i vetemlindur Bir dhe Fjale e Perendise qe je i pavdekshem, dhe denjove per shpetimin tone, te trupezohesh prej HyjIindeses se shenjte dhe gjithmone Virgjeres Mari, duke u bere njeri pa ndryshuar; qe u kryqezove, 0 Krisht Perendi, dhe shkele vdekjen me vdekje, qe Je nJe prej Trinise se Shenjte dhe lavderohesh bashke me Atin dhe me Shpirtin e Shenjte, shpetona.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconpositionantifon2}{
The Deacon goes and stands in front of the icon of Christ, looking towards the icon of the Mother of God, and after the completion of the Antiphon he comes and stands in his usual place, bows and says the Short Litany.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerantifon3.title.doc}{
Prayer of the Third Antiphon
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0401.text}{
Ti që na fale këto lutje, të cilat i bëjmë dhe i themi së bashku, dhe që premtove t'u japesh ç’të kërkojnë të bashkuarve në emrin tënd, qofshin këta edhe vetëm dy ose tre; Ti dhe tani plotësoi kërkesat e shërbetorëve në dobi të tyre, duke na falur në këtë botë njohjen e së vërtetës sate dhe duke na dhuruar ne botën tjetër jetë të amëshuar.
}%
\itId{sqi}{alb}{koas}{prayers}{exc03}{
Se Ti je Perëndi mëshirues dhe njeridashës dhe Ty ta drejtojmë lavdinë, Atit e Birit edhe Shpirtit të Shenjtë, tani e përherë e në jetë te jetëve.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.entersouth}{
The Deacon enters the Sanctuary by the south door.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.antifon3.title.doc}{
Third Antiphon and Entrance with the Holy Gospel
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.sundayantifon3}{
Then the Beatitudes, or the Third Antiphon, are sung. On Sundays the following Antiphon:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.verseantifon3}{
In the Mode of the week. Psalm 117
}%
\itId{sqi}{alb}{koas}{ps}{psa117.v1.text}{
Give thanks to the Lord, for he is good, for his mercy endures for ever.
}%
\itId{sqi}{alb}{koas}{ps}{psa117.v1.number}{
(117:1)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.resurrectionmode}{
Then the Resurrection Apolytikion of the current Mode.
}%
\itId{sqi}{alb}{koas}{ps}{psa117.v4.text}{
Let all those who fear the Lord say that he is good, that his mercy endures for ever.
}%
\itId{sqi}{alb}{koas}{ps}{psa117.v4.number}{
(117:4)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.resurrection}{
Then the Resurrection Apolytikion.
}%
\itId{sqi}{alb}{koas}{ps}{psa117.v24.text}{
This is the day which the Lord has made; let us rejoice and be glad in it.
}%
\itId{sqi}{alb}{koas}{ps}{psa117.v24.number}{
(117:24)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.smallentrance}{
While the Doxastikon of the Beatitudes, or the Third Antiphon, is being sung, the Priest and Deacon, standing in front of the Holy Table, make three bows; then the Priest takes the holy Gospel and gives it to the Deacon, who kisses the Priest’s hand. And so they come out through the north door, preceded by lights, and make the Little Entrance. Standing in the middle of the church they bow their heads.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconquietly}{
The Deacon, in a low voice, says:
}%
\itId{sqi}{alb}{koas}{prayers}{pet00}{
Let us pray to the Lord.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerentrance.title.doc}{
Prayer of the Entrance
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0501.text}{
O Zot Perendia yne, ti qe vendose ne qiejt legjione dhe armata engjejsh dhe kryeengjejsh per t'i sherbyer lavdise sate; bej qe bashke me hyrjen tone, te hyjne dhe engjej te shenjte, qe te meshojne bashke me ne dhe te lavderojne bashke me ne rniresine tende. Se Ty te perket tere lavdia, nderimi dhe adhurimi, Atit eBirit edhe Shpirtit te Shenjte, tani e perhere e ne jete te jeteve.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconquietly2}{
When the prayer is finished, the Deacon, in a low voice, says to the Priest:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0502.text}{
Beko o Zot, Hyrjen e shenjtë.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blessentrance}{
And the Priest, blessing the entrance, says, in a low voice:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0503.text}{
E bekuar është hyrja në shenjtëroren tënde, 0 Zot, gjithnjë; tani e perhërë e në jetë te jetëve. Amin.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.kissgospel}{
The Priest kisses the Gospel. The Deacon, standing in the middle of the church in front of the Priest and raising the sacred Gospel, says aloud:
}%
\itId{sqi}{alb}{koas}{prayers}{exc17}{
Urtësi!
}%
\itId{sqi}{alb}{koas}{prayers}{exc18}{
Drejt!
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.completeentrance}{
Then the Deacon, followed by the Priest, enters the Sanctuary through the Holy Doors and places the Gospel on the Holy Table.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.entrancechant}{
The People sing the Entrance Chant as follows:
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.EntranceHymn.text}{
Come, let us worship and fall down before Christ.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.sundaysofpascha}{
During Eastertide:
}%
\itId{sqi}{alb}{koas}{ps}{psa67.v27.text}{
Bless God in the Churches; the Lord from the fountains of Israel.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.kontakion1}{
The Apolytikia for the day and for the dedication of the Church are sung and after
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.kontakion2}{
the Kontakion of the Feast or Season.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.theotokoskontakion}{
Otherwise this Kontakion of the Mother of God. Mode 2:
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoTY.Key0408.text}{
Protection of Christians that cannot be put to shame, unfailing mediation with the Maker, do not despise the voices of us sinners as we pray; but, in your love, be quick to help us who cry to you with faith: Hasten to intercede, make speed to entreat, O Mother of God, for you ever protect those who honour you.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.kontakion3}{
After the Kontaion, the Deacon says:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.trisagionprayer.title.doc}{
Prayer of the Trisagion
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0601.text}{
O Perëndi e shenjtë, që prehesh nër të shenjtët, që himnohesh me zë trishënjtor nga serafimet dhe që lavdërohesh nga keruvimet e që adhurohesh nga çdo fuqi qiellore; ti që krijove gjithësinë nga e mosqena; që bëre njeriun simbas ikonës dhe shëmbëllesës sate, dhe e stolise me tërë dhuratat e tua; ti që i jep urtësi dhe mençuri atij që kërkon, dhe nuk e heq syrin nga mekatari, por caktove pendimin për shpëtim; ti që na bëre të denjë ne shërbëtorët e tu të përulur dhe te padenjë që të qëndrojmë ne këtë orë përpara lavdisë të altarit tënd të shenjtë dhe të të parashtrojmë adhurimin dhe lavdërimin që kemi për detyrë ndaj Teje. Ti, 0 Zot, prano dhe nga goja e neve mëkatarëve himnin trishenjtor, dhe vështrona me mirësinë tënde. Falna çdo faj të bërë me dashje ose pa dashje; shenjtërona shpirtrat dhe trupat tanë; dhe bëna te denjë që të të adhurojmë me shpresëtari tërë ditët e jetës sonë; me ndërmjetimet e Hyjlindëses së shenjtë dhe të gjithë shenjtorëve që të kanë pëlqyer që prej jete.
}%
\itId{sqi}{alb}{koas}{rubrical}{Aloud}{
(aloud)
}%
\itId{sqi}{alb}{koas}{prayers}{exc05a}{
Se i shenjtë je, 0 Perëndia ynë, dhe Ty ta drejtojmë lavdinë, Atit e Birit edhe Shpirtit të Shenjtë, tani e përherë,
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconkainyn}{
Deacon, coming near the Holy Doors and facing the People:
}%
\itId{sqi}{alb}{koas}{prayers}{exc05b}{
E në jetë të jetëve.
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.TrisagiosHymn.text}{
Shenjt Perëndi, Shenjt i fuqishëm, Shenjt i pa vdekshem, meshirona.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{doxapatrikainyn}{
Lavdi Atit e Birit edhe Shpirtit të Shenjtë. Tani e përherë e në jetë të jetëve. Amin.
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.TrisagiosHymn3.text}{
Shenjt I pavdekshëm,
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.TrisagiosHymn4.text}{
mëshirona.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0602.text}{
Fuqi!
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.trisagionclergy}{
The Priest and the Deacon also say the Trisagion, making three bows before the holy Table.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.command}{
Then the Deacon says to the Priest:
}%
\itId{sqi}{alb}{koas}{prayers}{KelefsonDespota}{
Udhëro, o Zot.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.approachthrone}{
And they go to the Throne. As they go the Priest says:
}%
\itId{sqi}{alb}{koas}{ps}{psa117.v26a.text}{
I bekuar është ai që vjen në emrin e Zotit.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0605.text}{
Beko, o Zot, fronin lart.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0606.text}{
I bekuar je mbi fronin e lavdisë së mbretërisë sate, ti që rri mbi Keruvimet, gjithnjë; tani e përherë e në jetë të jetevë. Amin.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.readings.title.doc}{
The Readings from the New Testament
}%
\itId{sqi}{alb}{koas}{actors}{PriestOrDeacon}{
*Deacon
}%
\itId{sqi}{alb}{koas}{prayers}{exc19}{
Le të vëmë re!
}%
\itId{sqi}{alb}{koas}{prayers}{pet31}{
Peace to all.
}%
\itId{sqi}{alb}{koas}{prayers}{res05}{
And to your spirit.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.prokimenontitle}{
Reader, coming into the middle of the church, says:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prokimenonmode}{
Prokeimenon of the Apostle. Mode… A Psalm of David.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.declaimprokimenon}{
The Reader and the Chanters declaim the Prokeimenon with its verse.
}%
\itId{sqi}{alb}{koas}{rubrical}{cl.eu.lichrysbasil.R009}{
The Reader reads the title of the Apostle.
}%
\itId{sqi}{alb}{koas}{rubrical}{cl.eu.lichrysbasil.R010}{
The Reader reads the Apostle, after which:
}%
\itId{sqi}{alb}{koas}{prayers}{epi02}{
Peace to you.
}%
\itId{sqi}{alb}{koas}{actors}{Chanters}{
Chanters
}%
\itId{sqi}{alb}{koas}{prayers}{Allilouia3.text}{
Alleluia, Alleluia, Alleluia.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.withverses}{
(with the verses).
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.censeapostolos}{
While the Alleluia is being sung the Deacon, taking the censer with incense, approaches the Priest, and having received a blessing for the incense he censes the book of the Gospel, the Holy Table all round, the whole sanctuary, the Priest and, coming out a little from the Holy Doors, the principal icons and the People.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.gospelprayer.title.doc}{
Prayer of the Gospel
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0704.text}{
O Zot njeridashës, bëj që të shkëlqejë në zemrat tona drita e kulluar e njohjes së hyjnisë sate, dhe çel syt e mendjes sonë për të kuptuar mësimet e tua ungjillore. Futna dhe frikën e porosive të tua të lumtura, që, pasi të shtypim të gjitha epshet trupore, të mundim të kalojmë një jetë shpirtërore, duke menduar dhe duke bërë të gjithaa ato që të pëlqejnë. Se ti je ndriçimi I shpirtrave dhe I trupave tanë, o Krisht Perëndi, dhe ty ta drejtojmë lavdinë, bashkë me Atin tënd pa fillim, dhe Shpiritin tënd të tërëshenjtë, të mirë dhe jetëbërës tani e perherë e në jetë të jetëve. Amin.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blessreader}{
The Deacon bows his head and says to the priest in a low voice:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.blessreader}{
Master, bless the herald of the Good Tidings of the Holy Apostle and Evangelist \color{red}N\color{black}.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blessreader2}{
The Priest blesses him, saying:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.blessreader2}{
May God, through the prayers of the holy, glorious Apostle and Evangelist \color{red}N \color{black}grant you to proclaim the word with much power, for the fulfilling of the Gospel of his Beloved Son, our Lord Jesus Christ.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.givegospel}{
And the Priest hands him the Gospel. The Deacon takes it, saying
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.gospelambon}{
And having kissed the Priest’s hand, goes out and preceded by lights makes his way to the Ambo.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.gospel.title.doc}{
The Holy Gospel
}%
\itId{sqi}{alb}{koas}{prayers}{gos02}{
Le të dëgjojmë Ungjillin e Shenjtë. 
}%
\itId{sqi}{alb}{koas}{rubrical}{name.period}{
\itRid{rubrical}{name}.
}%
\itId{sqi}{alb}{koas}{prayers}{DoxaSoiKyrie}{
Glory to you, O Lord, glory to you.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.readgospel}{
The *Deacon chants the Gospel for the day. When it is finished the Priest blesses the Deacon saying:
}%
\itId{sqi}{alb}{koas}{prayers}{gos04}{
Peace to you.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blesswithgospel}{
The Priest takes the Gospel from the Deacon, kisses it and blesses the people with it. He then replaces it on the Holy Table.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.kerygma.title.doc}{
The Homily
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.preach}{
Then the Preacher instructs the people in the word of God.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.beginlitany}{
Then the Deacon, standing in his usual place, says the following Litany of Fervent Supplication.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.greatlitany.title.doc}{
Litany of Fervent Supplication
}%
\itId{sqi}{alb}{koas}{prayers}{pet15}{
Le të themi të gjithë, me tërë shpirtin dhe me tërë mendjen tonë, le të themi:
}%
\itId{sqi}{alb}{koas}{prayers}{pet16}{
O Zot i gjithë-pusht-shëm, Perëndia e etërve tanë, të lutemi dëgjo e mëshiro.
}%
\itId{sqi}{alb}{koas}{prayers}{pet17}{
Mëshirona, o Perëndi, sipas mëshirës sate të madhe, të lutemi, dëgjo e mëshiro.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.thriceeach}{
(Tri herë. And so after the remaining petitions.)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet19lash.a}{
Also we pray for our Archbishop
}%
\itId{sqi}{alb}{koas}{rubrical}{name}{
Ν
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet19lash.b}{
and all our brotherhood in Christ.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet21lash.a}{
Lutemi edhe për mëshirë, jetë, paqë, shëndet, shpëtim, vështrim, ndjesë dhe falje të mëkateve të shërbëtorëve të Perëndisë, gjithë të krishterëve shpresëtarë dhe ortho--dhoksë, që banojnë dhe ndodhen në këtë qytet (ose manastir).
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet21lash.b}{
and for the servants of God
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet21lash.c}{
(Here he may name those for whom he has been asked to pray)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet21lash.d}{
and all who have asked for our prayers, unworthy though we are.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet22lash.a}{
Lutemi edhe për të lumturit dhe gjithmonë \textunderscore kujtu \textunderscore esh \textunderscore mit theme--lues të kësaj shtëpie të shenjtë, dhe për tërë etërit dhe vëllezërit tanë të parafjetur, orthodhoksë që prehen me shpresë këtu e kudo.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet22lash.b}{
and for the servants of God
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet22lash.c}{
(Here he may name those for whom he has been asked to pray)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet22lash.d}{
and that they may be pardoned all their offences, both voluntary and involuntary
}%
\itId{sqi}{alb}{koas}{prayers}{pet23}{
Lutemi edhe për ata që sjellin pemë dhe bëjnë punë të mira në këtë kishë të shenjtë dhe të gjithë--nderuar, që mundohen, që psalin dhe për popullin që qëndron rrotull, dhe pret prej Teje mëshirën e madhe dhe të pasur.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.ekteniaprayer.title.doc}{
Prayer of Supplication
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0801.text}{
Lord, our God, accept this fervent supplication from your servants, and have mercy on us according to the multitude of your mercy; and send down your pity on us and on all your people, who await your rich mercy.
}%
\itId{sqi}{alb}{koas}{prayers}{exc11}{
Se ti je Perëndi mëshirues dhe njeridashës dhe Ty ta drejtojmë lavdinë, Atit e Birit edhe Shpirtit të Shenjtë, tani e përherë e në jëtë të jetëve.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.catechumens}{
Then the Litany for the Catechumens, those preparing for Baptism.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.catechumens2}{
To each petition the People answer:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0901.text}{
Lutjuni Zotit, ju katikumenët.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0902.text}{
Ne besimtarët, le të lutemi për katikumenët.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0903.text}{
Që t'i mëshirojë Zoti.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0904.text}{
Që t'u mësojë fjalën e së vërtetës.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0905.text}{
Që t'u zbulojë Ungjillin e drejtësisë.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0906.text}{
Që t'i bashkojë me Kishën e shenjtë, të Katholike dhe Apostolike.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0907.text}{
Shpëtoi, mëshiroi, përkrahi dhe ruaji, o Perëndi, me hirin tënd.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0908.text}{
Ju katikumenët, kryet tuaj uljani Zotit.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayercatechumens.title.doc}{
Prayer for the Catechumens
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.beforeantimension.title.doc}{
(Before the Unfolding of the Antimension)
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0909.text}{
Lord, our God, dwelling on high and beholding things below, who for the salvation of mankind sent forth your only-begotten Son, our Lord and God, Jesus Christ, look upon your servants the catechumens, who have bowed their necks to you; and count them worthy in due time of the washing of rebirth, the forgiveness of sins and the garment of incorruption; unite them to your holy, Catholic and Apostolic Church, and number them with your chosen flock.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0910.text}{
That they also with us may glorify your all-honoured and majestic name, of Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.unfoldantimension}{
Then the Priest unfolds the Antimension on the Holy Table.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0911.text}{
As many as are catechumens, depart; catechumens, depart; as many as are catechumens, depart. None of the catechumens!
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgyfaithful.title.doc}{
The Liturgy of the Faithful
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0912.text}{
As many as are believers.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayer1faithful.title.doc}{
First Prayer of the Faithful
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.afterantimension.title.doc}{
(After the Unfolding of the Antimension)
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1001.text}{
We thank you, Lord God of the powers of heaven, for counting us worthy to stand even now before your holy altar and humbly to seek your compassion for our sins and for those committed in ignorance by the people. Receive our supplication, O God; make us worthy to offer you prayers and entreaties and unbloody sacrifices for all your people. And enable us, whom you have appointed to this your ministry by the power of your Holy Spirit, to invoke you at every time and place without blame and without condemnation, with the witness of a pure conscience, so that you may hear us and be merciful to us in the abundance of your goodness.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.prayer2faithful}{
And he enters the Sanctuary.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayer2faithful.title.doc}{
Second Prayer of the Faithful
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1002.text}{
Again and many times we fall down before you and pray you, who are good and the lover of mankind, that heeding our prayer you will cleanse our souls and bodies from every defilement of flesh and spirit, and will grant us to stand without guilt or condemnation before your holy altar. Give also to those who pray with us the grace of progress in right living, in faith and spiritual understanding. Grant that always worshipping you with fear and love, they may partake of your holy mysteries without guilt or condemnation, and be counted worthy of your heavenly kingdom.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1003.text}{
That being always guarded by your might, we may give glory to you, Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.cherubic.title.doc}{
Cherubic Hymn and Great Entrance with the Gifts of Bread and Wine
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.cherubic.title.toc}{
Cherubic Hymn and Great Entrance
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.cherubic}{
The Chanters begin the Cherubic Hymn to a slow and solemn melody, in the dominant Tone of the day:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1102.text}{
We, who in a mystery represent the Cherubim and sing the thrice-holy hymn to the life-giving Trinity, let us now lay aside every care of this life.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.prayercherubic}{
While it is being sung, the Priest, in front of the Holy Table, reads, in a low voice, the Prayer of the Cherubic Hymn.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayercherubic.title.doc}{
Prayer of the Cherubic Hymn
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1101.text.a}{
None of those who are entangled in carnal desires and pleasures is worthy to approach or draw near or minister to you, King of glory; for to serve you is great and awesome even for the heavenly powers. Yet on account of your inexpressible and boundless love for mankind you became man without change or alteration and were named our High Priest; and as Master of all you have committed to us the sacred ministry of this liturgy without shedding of blood.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1101.text.b}{
For you alone, Lord our God, are Ruler over all things in heaven and on earth, mounted on the throne of the Cherubim, Lord of the Seraphim and King of Israel, the only Holy One, resting in the holy place. Therefore I entreat you, who alone are good and ready to hear: Look upon me, your sinful and unprofitable servant, and purify my soul and heart from an evil conscience. By the power of your Holy Spirit enable me, clothed with the grace of the priesthood, to stand at this your Holy Table and celebrate the mystery of your holy and most pure Body and your precious Blood.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1101.text.c}{
For to you I come, bending my neck and praying: Do not turn away your face from me, nor reject me from among your children, but count me, your sinful and unworthy servant, worthy to offer these gifts to you. For you are the one who offers and is offered, who receives and is distributed, Christ our God, and to you we give glory, together with your Father, who is without beginning, and your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.prayercherubicsecret}{
After the prayer the Priest and the Deacon say the Cherubic Hymn three times, as follows:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.cherubic2}{
For we are about to receive the King of all, invisibly escorted by the angelic hosts. Alleluia.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.censeatcherubikon}{
Then the Priest, or Deacon, takes the censer and censes the Holy Table, the Sanctuary, the principal icons and the People, coming out a little from the holy Doors.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.anastasin}{
In a low voice he says, if it is Sunday,
}%
\itId{sqi}{alb}{koas}{ho.s03}{hoMA.SunPostGospel.text.a}{
Having seen the Resurrection of Christ...,
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.andpsalmor1}{
and Psalm 50, excluding the last two verses which begin,
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.andpsalmor2}{
Do good, Lord, ...to Sion.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.andpsalmor3}{
If it is not a Sunday he says,
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{DefteProskinisomen0}{
Come let us worship...
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.andpsalmor4}{
three times and then Psalm 50 as above.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.forgive}{
Then he enters the Sanctuary and puts away the censer. Then both of them, coming in front of the Holy Table make three bows, and say quietly troparia of compunction. They kiss the Antimension and the Holy Table, bow again and then turn to the people and bow to them, saying:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.forgive}{
Forgive me,
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.orsimilar}{
or similar words.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.approachprothesis}{
They go to the table of the Prothesis, and having made three bows they kiss the covered Holy Gifts, saying:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.preparation.mercy}{
God, cleanse me a sinner.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.eparon}{
Then the Deacon says to the Priest:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.eparon}{
Master, lift up.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.wearaer}{
The Priest lifts the Aer and places it on the shoulders of the Deacon, saying:
}%
\itId{sqi}{alb}{koas}{ps.kenya.alt}{psa133.v2alt2.text}{
Lift up your hands to the holy place and bless the Lord.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.psa133.v2.fullattribution}{
(Psalm 133:2)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.takegifts}{
Then he gives the Deacon the Paten, while he himself takes the Chalice.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.procession}{
When the Chanters reach the end of the first part of the Cherubic Hymn, the Deacon and the Priest come out from the north door of the Sanctuary, preceded by exapteryga, lights and incense, as they make the Great Entrance. As they process they proclaim, one after the other:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1110.text}{
May the Lord God remember you all in his Kingdom always, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{actors}{Chanter}{
Chanter
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.completehymn}{
And they complete the Cherubic Hymn:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.enteraltar}{
The Priest and Deacon enter the Sanctuary.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconright}{
The Deacon, stands to the right in front of the Holy Table and says to the Priest as he enters
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1114.text}{
May the Lord God remember your priesthood in his Kingdom, always, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.priestresponse}{
And the Priest, as he enters, says to him
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.holydiaconate}{
May the Lord God remember your diaconate in his Kingdom, always, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.placegiftsaltar}{
Then the Priest places the Chalice on the Holy Table, takes the Paten from the Deacon and places it to the left of the Chalice, saying
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.noblejoseph}{
The noble Joseph, taking your most pure Body from the Tree, wrapped it in pure linen with sweet spices and laid it for burial in a new grave.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.covergiftsaer}{
Then he takes the covers from the sacred Paten and the Holy Chalice and lays them to one side on the Holy Table. He takes the Aer from the shoulders of the Deacon, holds it over the censer and lays it over the Chalice and Paten. Then he takes the censer and censes the Gifts three times, as the Deacon says:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1116.text}{
Do good, Master.
}%
\itId{sqi}{alb}{koas}{ps}{psa50.v20.text}{
Do good to Sion, Lord, in your good pleasure, and let the walls of Jerusalem be rebuilt.
}%
\itId{sqi}{alb}{koas}{ps}{psa50.v21a.text}{
Then you will be well pleased with a sacrifice of righteousness, oblation and whole burnt offerings.
}%
\itId{sqi}{alb}{koas}{ps}{psa50.v21b.text}{
Then they will offer calves upon your altar.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.psa50.v20.v21.fullattribution}{
(Psalm 50:20-21)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.rememberpriest}{
He puts away the censer and, bowing his head, says to the Deacon
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1118.text}{
Remember me, brother and fellow celebrant.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.praypriest}{
Pray for me, brother and fellow celebrant.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1120.text}{
The Holy Spirit will come upon you, and the power of the Most High will overshadow you.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1121.text}{
The Spirit himself will concelebrate with us all the days of our life.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.rememberdeacon}{
Deacon, bowing his head, says to the Priest
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1122.text}{
Remember me, holy Master.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key0106.text}{
May the Lord God remember you in his Kingdom always, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.andsaying}{
And the Deacon, having answered
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.beginlitanygifts}{
kisses the Priest’s right hand and goes out and stands in his usual place and says the Litany of the Precious Gifts.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.litanygifts.title.doc}{
Litany of the Precious Gifts
}%
\itId{sqi}{alb}{koas}{prayers}{pet24}{
Let us complete our prayer to the Lord.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.eachpetition2}{
And so after each of the following petitions.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1201.text}{
For the precious gifts here set forth, let us pray to the Lord.
}%
\itId{sqi}{alb}{koas}{prayers}{pet25m}{
That the whole day may be perfect, holy, peaceful and sinless, let us ask of the Lord.
}%
\itId{sqi}{alb}{koas}{prayers}{res02}{
Grant this, O Lord.
}%
\itId{sqi}{alb}{koas}{prayers}{pet26}{
An angel of peace, a faithful guide, a guardian of our souls and bodies, let us ask of the Lord.
}%
\itId{sqi}{alb}{koas}{prayers}{pet27}{
Pardon and forgiveness of our sins and offences, let us ask of the Lord.
}%
\itId{sqi}{alb}{koas}{prayers}{pet28}{
Those things that are good and profitable for our souls, and peace for the world, let us ask of the Lord.
}%
\itId{sqi}{alb}{koas}{prayers}{pet29}{
That we may live out the rest of our days in peace and repentance, let us ask of the Lord.
}%
\itId{sqi}{alb}{koas}{prayers}{pet30}{
A Christian end to our life, painless, unashamed and peaceful, and a good defence before the dread judgement seat of Christ, let us ask.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1202.title.doc}{
Prayer of Offering
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1202.text}{
Lord, God, the Almighty, who alone are holy and who accept a sacrifice of praise from those who call on you with all their heart, accept also the supplication of us sinners, bring us to your holy altar, and enable us to offer you gifts and spiritual sacrifices for our sins and those committed in ignorance by the people. Count us worthy to find grace in your sight, that our sacrifice may be well pleasing to you and that the good Spirit of your grace may rest on us and on these gifts here set forth, and on all your people.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1203.text}{
Through the compassion of your only-begotten Son, with whom you are blessed, together with your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1204.text}{
Let us love one another, that with one mind we may confess:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1205.text}{
Father, Son and Holy Spirit, Trinity consubstantial and undivided.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.agapwse}{
The Priest bows three times and kisses the Aer over the Gifts, saying in a low voice:
}%
\itId{sqi}{alb}{koas}{ps}{psa17.v2.text}{
I will love you, Lord, my strength.
}%
\itId{sqi}{alb}{koas}{ps}{psa17.v3a.text}{
The Lord is my firm foundation, my refuge and my deliverer.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.kissofpeace}{
Likewise the Deacon, standing in his place, bows three times and kisses the Cross on his orarion. At a concelebrated Liturgy the Priests here exchange the Kiss of Peace, the senior saying: \color{black}Christ is in our midst\color{red}, to which the junior answers: \color{black}He is and will be.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconkiss}{
If there is more than one Deacon they also exchange the Kiss with one another in the same way on the solea.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.creed.title.doc}{
The Creed
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1208.text}{
The doors, the doors. With wisdom let us attend.
}%
\itId{sqi}{alb}{koas}{prayers}{Pistevo.text.a}{
I believe in one God, * Father, Almighty, * Maker of heaven and earth, * and of all things visible and invisible.
}%
\itId{sqi}{alb}{koas}{prayers}{Pistevo.text.b}{
And in one Lord, Jesus Christ,* the only-begotten Son of God, * begotten from the Father * before all ages, * Light from Light, * true God from true God, * begotten * not made, * consubstantial with the Father,* through him all things were made. * For our sake and for our salvation * he came down from heaven, * and was incarnate from the Holy Spirit * and the Virgin Mary * and became man. * He was crucified also for us under Pontius Pilate,* and suffered and was buried; * he rose again on the third day, * in accordance with the Scriptures, * and ascended into heaven * and is seated at the right hand of the Father. * He is coming again in glory * to judge the living and the dead, * and his kingdom will have no end.
}%
\itId{sqi}{alb}{koas}{prayers}{Pistevo.text.c}{
And in the Holy Spirit, * the Lord, * the Giver of life, * who proceeds from the Father, * who together with Father and Son is worshipped * and together glorified; * who spoke through the Prophets.
}%
\itId{sqi}{alb}{koas}{prayers}{Pistevo.text.d}{
In one, Holy, * Catholic and Apostolic Church. * I confess one Baptism * for the forgiveness of sins. * I await the resurrection of the dead * and the life of the age to come. Amen.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.waveaer}{
While the Creed is being said the Priest lifts the Aer and waves it above the Chalice and Paten. At the words \color{black}and ascended into heaven…, \color{red}he kisses the Cross in the middle of it, folds it and puts it to one side with the veils.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1300.title.doc}{
The Holy Oblation
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1301.text}{
Let us stand with awe; let us stand with fear; let us attend to the holy oblation, that in peace we may offer,
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1302.text}{
Mercy, peace: a sacrifice of praise.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconreturn}{
The Deacon re-enters the Sanctuary.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.priestblessing}{
(blessing the People with his hand)
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1303.text}{
The grace of our Lord Jesus Christ, and the love of God the Father, and the communion of the Holy Spirit be with you all.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1304.text}{
And with your spirit.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.liftinghands}{
(raising his hands)
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1305.text}{
Let our hearts be on high.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1306.text}{
We have them with the Lord.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1307.text}{
Let us give thanks to the Lord.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1308.text}{
It is right and fitting.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1309.text}{
It is right and fitting to hymn you, to bless you, to praise you, to give you thanks, to worship you in every place of your dominion; for you are God, ineffable, incomprehensible, invisible, inconceivable, ever existing, eternally the same; you and your only-begotten Son and your Holy Spirit. You brought us out of non-existence into being, and when we had fallen you raised us up again, and left nothing undone until you had brought us up to heaven and had granted us your Kingdom that is to come. For all these things we give thanks to you, and to your only-begotten Son and your Holy Spirit; for all the benefits that we have received, known and unknown, manifest and hidden. We thank you also for this liturgy which you have been pleased to accept from our hands, though there stand around you thousands of archangels and tens of thousands of angels, the Cherubim and the Seraphim, six-winged and many-eyed, soaring aloft upon their wings,
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1310.text}{
singing, crying, shouting the triumphal hymn, and saying:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1311.text}{
Holy, holy, holy, Lord Sabaoth; heaven and earth are full of your glory. Hosanna in the highest. Blessed is he who comes in the name of the Lord. Hosanna in the highest.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.removestar}{
The Deacon takes the Star from the Paten, making the sign of the Cross with it over the Paten, kisses it and lays it aside on the Holy Table.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1312.text}{
With these blessed Powers, Master, Lover of mankind, we also cry aloud and say: Holy are you and all-holy, you and your only-begotten Son and your Holy Spirit. Holy are you and all-holy, and magnificent is your glory. This is how you loved your world: you gave your only-begotten Son, so that everyone who believes in him might not perish, but have eternal life. And, when he had come and had fulfilled the whole dispensation for us, in the night in which he was given up, or rather gave himself up, for the life of the world, he took bread in his holy, most pure and unblemished hands and, when he had given thanks and had blessed, sanctified and broken it, gave it to his holy Disciples and Apostles, saying:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1313.text}{
Take, eat; this is my body, which is broken for you, for the forgiveness of sins.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1314.text}{
Likewise after supper he also took the cup, saying:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1315.text}{
Drink from this, all of you; this is my blood of the New Covenant, which is shed for you and for many for forgiveness of sins.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1316.text}{
Remembering therefore this our Saviour’s command and all that has been done for us: the Cross, the Tomb, the Resurrection on the third day, the Ascension into heaven, the Sitting at the right hand, the second and glorious Coming again,
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.exaltgifts}{
The *Deacon crosses his hands and elevates the Chalice and Paten.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.tasa}{
offering you your own from your own — in all things and for all things —
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.seimnumen}{
we praise you, we bless you, we give thanks to you, O Lord, and we pray to you, our God.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.bowinghead}{
The Priest, bowing his head, says
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1319.text}{
Also we offer you this spiritual worship without shedding of blood, and we ask, pray and implore you: send down your Holy Spirit upon us and upon these gifts here set forth,
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.pointbread}{
Then the Deacon, pointing to the holy Bread with his orarion, says
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.changebread}{
Master, bless the holy Bread.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.changebread}{
The Priest blesses the holy Bread, saying:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1321.text}{
and make this bread the precious Body of your Christ,
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.pointchalice}{
Then the Deacon, pointing to the Chalice with his orarion, he says
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.changewine}{
Master, bless the holy Cup.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blesschalice}{
The Priest blesses the Chalice, saying:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1323.text}{
and what is in this Cup the precious Blood of your Christ,
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blessboth}{
Then he, pointing to them both, says
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.blessboth}{
Master, bless them both.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.epiclesis}{
Priest, blessing both the Chalice and Paten, says:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1325.text}{
changing them by your Holy Spirit,
}%
\itId{sqi}{alb}{koas}{prayers}{res10}{
Amen, Amen, Amen.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.forvigilance}{
The Priest, bowing profoundly, continues
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1326.text}{
so that those who partake of them may obtain vigilance of soul, forgiveness of sins, communion of the Holy Spirit, fulness of the Kingdom of heaven, freedom to speak in your presence, not judgement or condemnation. Also we offer you this spiritual worship for those who have gone to their rest in faith, Forefathers, Fathers, Patriarchs, Prophets, Apostles, Preachers, Evangelists, Martyrs, Confessors, Ascetics and every righteous spirit made perfect in faith;
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.censemegalynarion}{
As he censes from in front of the holy Table, the Priest says, aloud:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1327.text}{
Above all for our all-holy, pure, most blessed and glorious Lady, Mother of God and Ever-Virgin, Mary.
}%
\itId{sqi}{alb}{koas}{prayers}{AxionEstin.text}{
It is truly right to call you blessed, who gave birth to God, ever-blessed and most pure, and Mother of our God. Greater in honour than the Cherubim and beyond compare more glorious than the Seraphim, without corruption you gave birth to God the Word; truly the Mother of God, we magnify you.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.megalynarionfeast}{
If it is a feast of the Lord or of the Mother of God, or its leave-taking, the Irmos of the 9th Ode of the Canon is sung instead.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.censecommemmorate}{
The Priest gives the censer to the Deacon, who censes around the Holy Table and, in a low voice, remembers to himself those whom he wishes of the dead, while the Priest continues:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1329.text.a}{
For the holy Prophet, Forerunner and Baptist John, the holy, glorious and all-praised Apostles, for Saint \color{red}N\color{black}, whose memory we keep today, and for all your Saints, at whose prayers visit us, O God.
}
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1329.text.b}{
Remember too all those who have fallen asleep in hope of resurrection to eternal life \color{red}(N \color{black} and \color{red}N)\color{black}, and give them rest where the light of your countenance watches.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1329.text.c}{
Also we beseech you: Remember, Lord, all Orthodox bishops, who rightly discern the word of your truth, the whole order of presbyters, the diaconate in Christ, all the clergy and the whole monastic order.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1329.text.d}{
Also we offer you this spiritual worship for the whole world, for the holy, Catholic and Apostolic Church, for those who live in chastity and holiness of life; for our faithful Christian rulers, and all their household. Grant them, Lord, a peaceful reign, so that in their tranquillity we too may live calm and peaceful lives in godliness and holiness.
}%
\itId{sqi}{alb}{koas}{actors}{Clergy}{
Clergy
}%
\itId{sqi}{alb}{koas}{client}{euLI.Key1330a.text}{
First of all, remember, Lord,
}%
\itId{sqi}{alb}{koas}{client}{cl.bishop1.rank}{
our Archbishop,
}%
\itId{sqi}{alb}{koas}{client}{cl.bishop1.name.p}{
\color{red}N\color{black},
}%
\itId{sqi}{alb}{koas}{client}{euLI.Key1330b.text}{
and grant that he may serve your holy churches in peace, safety, honour, health, and length of days, rightly discerning the word of your truth.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.wote}{
The *Deacon, standing at the Holy Door, recites the Diptychs of the living and then exclaims:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1331.text}{
And those whom each one has in mind, and each and all.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1332.text}{
And each and all.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1333.text}{
Remember, Lord, this city in which we dwell, and every city, town and village, and the faithful who dwell in them. Remember, Lord, those who travel by land, air, or water, the sick, the suffering, those in captivity, and their safety and salvation. Remember, Lord, those who bring offerings, those who care for the beauty of your holy churches, and those who remember the poor, and send down upon us all your rich mercies.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1334.text}{
And grant that with one voice and one heart we may glorify and praise your all-honoured and majestic name, of Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blessmercy}{
The Priest blesses the People with his hand, saying:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1335.text}{
And the mercies of our great God and Saviour, Jesus Christ, shall be with all of you.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1336.text}{
And with your spirit.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.litanylordsprayer.title.doc}{
Litany Before the Lord's Prayer
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.litanylords}{
The Deacon comes out and stands in his usual place.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1401.text}{
Having commemorated all the saints, again and again in peace let us pray to the Lord.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1402.text}{
For the precious gifts here set forth and sanctified, let us pray to the Lord.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1403.text}{
That our God, who loves mankind, having accepted them on his holy and immaterial Altar above the heavens, as a savour of spiritual fragrance, may send down upon us in return his divine grace and the gift of the Holy Spirit, let us pray.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1404.text}{
Having asked for the unity of the faith and the communion of the Holy Spirit, let us entrust ourselves and one another and our whole life to Christ, our God.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1405.text}{
To you, Master, Lover of mankind, we entrust our whole life and our hope, and we entreat, pray and implore you: count us worthy to partake of your heavenly and awesome Mysteries at this sacred and spiritual Table with a pure conscience, for the forgiveness of sins and pardon of offences, for communion of the Holy Spirit, for inheritance of the Kingdom of heaven and for confidence before you; not for judgement or condemnation.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1406.text}{
And count us worthy, Master, with confidence and without condemnation to dare to call upon you, the God of heaven, as Father, and to say:
}%
\itId{sqi}{alb}{koas}{titles}{KyriakiProsefchi.title.doc}{
The Lord's Prayer
}%
\itId{sqi}{alb}{koas}{prayers}{PaterImon.text}{
Our Father, in heaven, * may your name be sanctified, * your kingdom come, * your will be done * on earth as in heaven. * Give us today our daily bread, * and forgive us our debts, * as we forgive our debtors, * and do not lead us into temptation, * but deliver us from the evil one.
}%
\itId{sqi}{alb}{koas}{prayers}{exc20}{
For yours is the kingdom, the power and the glory, Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{prayers}{pet32}{
Let us bow our heads to the Lord.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1407.text}{
We thank you, King invisible, who by your boundless power created all things, in the abundance of your mercy bringing them into being out of nothing. Look down from heaven, Master, on those who have bowed their heads to you; for they have bowed not to flesh and blood, but to you, the God before whom we stand in awe. Make smooth, then, our path for our good, Master, through what lies before us, according to the need of each: sail with those sail, journey with those who journey, heal the sick, for you are the physician of our souls and bodies.
}%
\itId{sqi}{alb}{koas}{prayers}{exc07a}{
Through the grace and compassion and love towards mankind of your only-begotten Son, with whom you are blessed, together with your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.holycommunion.title.doc}{
Holy Communion of the Clergy and People
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1409.text}{
Give heed, Lord Jesus Christ our God, from your holy dwelling-place and from the glorious throne of your kingdom; and come to sanctify us, you who are enthroned on high with the Father and invisibly present here with us. And with your mighty hand grant communion in your most pure Body and precious Blood to us, and through us to all the people.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.bowcommunion}{
Then the Priest, and the Deacon, in his usual place, bow three times, saying
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.holyforholy}{
The Priest elevates the Holy Bread and says aloud:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1410.text}{
The Holy Things for the Holy.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1411.text}{
One is holy, one is Lord: Jesus Christ, to the glory of God the Father. Amen.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.communionhymn}{
The Singers continue with the Communion Chant.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.communionhymnsunday}{
On Sundays:
}%
\itId{sqi}{alb}{koas}{ps}{psa148.v1.text}{
Praise the Lord from heaven, praise him in the highest.
}%
\itId{sqi}{alb}{koas}{titles}{Allilouia.title.doc}{
Alleluia.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.communionhymnfullattribution}{
(Psalm 150:1)
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.communionhymnotherdays}{
On other days as appointed in the Typikon.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.crossorarion}{
The Deacon enters the Sanctuary, ties his orarion in the form of a Cross and standing on the right of the Priest says
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1501.text}{
Master, break the holy Bread.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.breakbread}{
The Priest divides the Lamb into four parts, saying
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1502.text}{
The Lamb of God is broken and distributed, broken yet not divided, ever eaten yet never consumed, but sanctifying those who partake.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.placecrosswise}{
He arranges them on the Paten in the form of a Cross, thus:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.fillchalice}{
The Deacon points to the Chalice with his Orarion and says
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1503.text}{
Master, fill the holy Cup.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.ic}{
The Priest takes the portion of the Lamb stamped with the letters \color{black}IC \color{red}and makes the sign of the Cross with it above the holy Chalice and places it in it, saying
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pliroma}{
Fullness of the Holy Spirit.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.takezeon}{
He takes the hot water and says to the Priest
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1505.text}{
Master, bless the hot water.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blesszeon}{
The Priest blesses it, saying
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1506.text}{
Blessed is the fervour of your holy things, always, now and for ever, and to the ages of ages. Amen.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.pourzeon}{
The Deacon pours the hot water into the Chalice in the form of a cross, saying
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.zesis}{
Fervour of the Holy Spirit. Amen.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.approachbody}{
The Priest asks the forgiveness of those in the Sanctuary and the rest of the church. Then he approaches the Holy Table and says
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1509.text}{
Behold, I draw near to Christ, our immortal King and God.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.xc}{
He takes a portion of the precious Body of Christ, from the part stamped with the letters \color{black}XC\color{red}, and says
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1510.text}{
To me the unworthy Priest \color{red}[\color{black}and Monk\color{red}] N \color{black}is granted communion in the precious and all-holy Body of our Lord and God and Saviour, Jesus Christ, for forgiveness of my sins and everlasting life.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.wipehand}{
And he receives the Holy Bread with fear and great care; and having wiped his hand over the Paten with the sponge he says
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.deaconcommune}{
Deacon, draw near.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconcommune}{
The Deacon, as he approaches, says:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1512.text}{
Behold, I draw near to Christ, our immortal King and God. Grant me, Master, communion in the precious and all-holy Body of our Lord and God and Saviour, Jesus Christ, for forgiveness of my sins and everlasting life.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconcommune2}{
The Priest gives the Deacon a portion of the Holy Bread and says
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1513.text}{
To you, most devout Deacon \color{red}[\color{black}and Monk\color{red}] N \color{black}is granted communion in the precious and all-holy Body of our Lord and God and Saviour, Jesus Christ, for forgiveness of your sins and everlasting life.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconcommune3}{
The Deacon kisses the Priest’s hand, goes to the back of the Holy Table, and communicates like the Priest.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.chaliceandcloth}{
The Priest takes the Chalice, with the Communion cloth, and says
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1515.text}{
To me the unworthy Priest \color{red}[\color{black}and Monk\color{red}] N \color{black}is granted communion in the precious and all-holy Blood of our Lord and God and Saviour, Jesus Christ, for forgiveness of my sins and everlasting life.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.drinkthrice}{
He drinks three times from the Chalice, wipes his lips and the Chalice with the cloth, and kisses the Chalice, saying
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1516.text}{
This has touched my lips: it will take away my iniquities and cleanse my sins.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconcommune4}{
Then he says to the Deacon
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.deaconcommune2}{
Deacon, again draw near.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconcommune5}{
The Deacon, having carefully wiped his hand over the Paten with the Sponge, approaches, saying
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.approachagain}{
Behold, again I draw near to Christ, our immortal King and God.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1518.text}{
Grant me, Master, communion in the precious and all-holy Blood of our Lord and God and Saviour, Jesus Christ, for forgiveness of my sins and everlasting life.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.etimetadidotai}{
To you, most devout Deacon \color{red}[\color{black}and Monk\color{red}] N \color{black}is granted communion in the precious and all-holy Blood of our Lord and God and Saviour, Jesus Christ, for the forgiveness of your sins and for eternal life.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.deaconcommune6}{
Once the Deacon has communed, the Priest says
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1520.text}{
This has touched your lips: it will take away your iniquities and cleanse your sins.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.nika}{
The Deacon divides the two remaining parts of the Lamb (\color{black}NI \color{red}and \color{black}KA\color{red}) into small pieces and places them in the Chalice, which he covers with the Communion cloth.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.distribution.title.doc}{
Distribution of Holy Communion
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.approach}{
The Holy Doors are opened and the Priest hands the Chalice to the Deacon, who comes out through the Holy Doors, raises the Chalice, and says:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1526.text}{
With fear of God, with faith and love, draw near.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.godisthelord}{
Blessed is he who comes in the name of the Lord. The Lord is God and has appeared to us.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.distributionprayer}{
The Deacon hands the Chalice to the Priest, who gives Communion to the People, saying to each communicant:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.distributionprayershort}{
The Body and Blood of Christ, for the forgiveness of sins and everlasting life.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.toudeipnou}{
While Communion is being given the following is sung, as many times as is necessary for the number of communicants:
}%
\itId{sqi}{alb}{koas}{ho.s21}{hoPCPrayer.TouDeipnouSou.text}{
Of your mystical Supper, Son of God, today receive me as a communicant; for I will not speak of the Mystery to your enemies; I will not give you a kiss, like Judas; but like the Thief I confess you: Remember me, Lord, in your Kingdom.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.paschalcommunion}{
During Eastertide (in some places, always):
}%
\itId{sqi}{alb}{koas}{pe.d00P}{pePA.CommunionHymn.text}{
Receive the Body of Christ; taste from the immortal fount.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.alleluia}{
Alleluia, Alleluia, Alleluia.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.replacechalice}{
When all have communicated, the Priest hands the Chalice to the Deacon, who places it on the holy Table again.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blesshand}{
The Priest blesses the People with his hand, saying:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1529.text}{
O God, save your people, and bless your inheritance.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1530.text}{
We have seen the true light; we have received the heavenly Spirit; we have found the true faith, as we worship the undivided Trinity; for the Trinity has saved us.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.iflordsfeast}{
On feasts of the Lord and their leave-taking the Apolytikion of the Feast is sung;
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.paschal}{
during Eastertide \color{black}Christ has risen from the dead...
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.wipeparticles}{
Meanwhile the Deacon holding the Paten above the Chalice carefully wipes the particles remaining on the Paten into the Chalice, saying:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1525.text}{
Wash away, Lord, by your holy Blood the sins of your servants here remembered, through the prayers of the Mother of God and all your Saints. Amen.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.eparon.b}{
The Deacon says to the Priest:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1601.text}{
Master, exalt.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.censeexalt}{
The Priest censes the Chalice three times, saying each time:
}%
\itId{sqi}{alb}{koas}{ps}{psa56.v6.text}{
Be exalted, O God, above the heavens; and your glory over all the earth.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.showcoversstar}{
Then he gives the Paten, with the covers and the Star, to the Deacon, who shows them to the People and then takes them to the table of the Prothesis, going round behind the Holy Table. He then unties his orarion.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blessed}{
The Priest bows, takes the Chalice and says in a low voice:
}%
\itId{sqi}{alb}{koas}{prayers}{EvlogitosOTheosImon.text}{
Blessed is our God.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.blessed2}{
Αnd then turns to the People, shows them the Chalice and continues, aloud:
}%
\itId{sqi}{alb}{koas}{prayers}{PantoteNyn.text}{
Always, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1603.text}{
Let our mouth be filled with your praise, O Lord, that we may sing of your glory, for you have counted us worthy to partake of your holy, divine, immortal and life-giving Mysteries; keep us in your holiness, that we may meditate on your righteousness all the day long. Alleluia, alleluia, alleluia.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.thanksdismissal.title.doc}{
Thanksgiving and Dismissal
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.foldantimension}{
The Priest places the Chalice on the Prothesis, returns, and folds up the Antimension, after making sure that no crumb remains.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.havingpartaken}{
The *Deacon comes to his usual place and says:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1604.text}{
Stand upright. Having received the divine, holy, pure, immortal, heavenly, life-giving and dread Mysteries of Christ, let us give worthy thanks to the Lord.
}%
\itId{sqi}{alb}{koas}{rubrical}{Or}{
Or
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1605.text}{
Having asked that the whole day may be perfect, holy, peaceful and sinless, let us entrust ourselves and one another and our whole life to Christ our God.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1606.title.doc}{
Prayer of Thanksgiving
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1606.text}{
We thank you, Lord, lover of mankind, benefactor of our souls, that you have counted us worthy today of your heavenly and immortal Mysteries. Make straight our way, establish us all in the fear of you, watch over our life, and make firm our steps, through the prayers and intercessions of the glorious Mother of God and Ever-Virgin Mary, and of all your Saints.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.crossantimensiongospel}{
Taking the holy Gospel, he makes the sign of the Cross with it over the folded Antimension and says aloud:
}%
\itId{sqi}{alb}{koas}{prayers}{exc24}{
For you are our sanctification, and to you we give glory, Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1700.title.doc}{
Dismissal
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1701.text}{
Let us go forth in peace.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.lordsname}{
In the name of the Lord.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.ambonprayer}{
The Priest comes out through the Holy Doors and reads aloud:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.ambonprayer.title.doc}{
Prayer Behind the Ambo
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1702.text}{
O Lord, you bless those who bless you, and sanctify those who have put their trust in you: save your people and bless your inheritance; protect the fullness of your Church; sanctify those who love the beauty of your house; glorify them in return by your divine power, and do not forsake us who hope in you. Give peace to your world, to your churches, to the priests, to our rulers, and to all your people. For every good gift and every perfect gift is from above, coming down from you, the Father of lights; and to you we give glory, thanksgiving and worship, Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{ps}{psa112.v2alt1.text}{
Blessed be the name of Lord, from this time forth and for evermore.
}%
\itId{sqi}{alb}{koas}{rubrical}{Thrice}{
(three times).
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.pliromanomou}{
The Priest returns to the Sanctuary through the Holy Doors, goes to the table of the Prothesis and says, in a low voice:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1704.text}{
Christ, our God, the fulfilment of the Law and the Prophets, you have fulfilled all the Father’s dispensation. Fill our hearts with joy and gladness, always, now and for ever, and to the ages of ages. Amen.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.evlogiakyriou}{
The Priest, coming out through the Holy Doors and blessing the People, says:
}%
\itId{sqi}{alb}{koas}{prayers}{pet37}{
The blessing of the Lord and his mercy be upon you, by his grace and love for mankind, always, now and for ever, and to the ages of ages.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{DoxaSoiOTheos2}{
Glory to you, O God, our hope, glory to you.
}%
\itId{sqi}{alb}{koas}{actors}{Reader}{
Reader
}%
\itId{sqi}{alb}{koas}{prayers}{res06}{
Lord, have mercy. Lord, have mercy. Lord, have mercy.
}%
\itId{sqi}{alb}{koas}{prayers}{res13}{
Holy Master, bless.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.dis.oanastas}{
May
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.sundaydismissal}{
(on Sundays: he who rose from the dead,)
}%
\itId{sqi}{alb}{koas}{dismissals}{dis01}{
Christ, our true God,
}%
\itId{sqi}{alb}{koas}{dismissals}{dis02}{
through the prayers of his all pure and holy Mother,
}%
\itId{sqi}{alb}{koas}{dismissals}{dis03}{
by the power of the precious and life-giving Cross,
}%
\itId{sqi}{alb}{koas}{dismissals}{dis04}{
through the protection of the honoured, Bodiless Powers of heaven,
}%
\itId{sqi}{alb}{koas}{dismissals}{dis05}{
through the intercessions of the honoured, glorious Prophet, Forerunner and Baptist, John,
}%
\itId{sqi}{alb}{koas}{dismissals}{dis06}{
of the holy, glorious and all-praised Apostles,
}%
\itId{sqi}{alb}{koas}{dismissals}{dis07}{
of the holy, glorious and triumphant Martyrs,
}%
\itId{sqi}{alb}{koas}{dismissals}{li.dis.fathersmothers}{
of our venerable and God-bearing Fathers and Mothers,
}%
\itId{sqi}{alb}{koas}{dismissals}{li.dis.ofsaint}{
of Saint \color{red}N \color{black}
}%
\itId{sqi}{alb}{koas}{dismissals}{li.dis.oftemple}{
\color{red}(of the Church)\color{black},
}%
\itId{sqi}{alb}{koas}{dismissals}{li.dis.chrysostom}{
of our Father among the Saints John Chrysostom, Archbishop of Constantinople,
}%
\itId{sqi}{alb}{koas}{dismissals}{dis09}{
of the holy and righteous forebears of God, Joachim and Anna,
}%
\itId{sqi}{alb}{koas}{dismissals}{li.dis.ofday}{
\color{red}(of the day)
}%
\itId{sqi}{alb}{koas}{dismissals}{li.dis.memory}{
\color{black}whose memory we keep today,
}%
\itId{sqi}{alb}{koas}{dismissals}{dis10}{
and all the Saints,
}%
\itId{sqi}{alb}{koas}{dismissals}{dis88}{
have mercy on us and save us, for he is good and loves mankind.
}%
\itId{sqi}{alb}{koas}{prayers}{DiEfchonPateron.text}{
Through the prayers of our holy fathers, Lord Jesus Christ, our God, have mercy upon us.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.finalblessing}{
The Priest, blessing the People, says:
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1707.text}{
May the holy Trinity protect you all.
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1706.text}{
O Lord, protect the one who blesses us and sanctifies us, for many years.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.giveantidoron}{
The Priest distributes the Antidoron, saying to each recipient:
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.blessingmercy}{
May the blessing and mercy of the Lord come upon you.
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.end.title.doc}{
The End of the Divine Liturgy of John Chrysostom
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgy.title.doc}{
\itRid{pub.priest.servicebook}{li.liturgy.title.cover}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgy.title.header}{
\itRid{pub.priest.servicebook}{li.liturgy.title.toc}
}%
\itId{sqi}{alb}{koas}{client}{li.hierarchical.sponsor.title.doc}{
\itRid{client}{li.hierarchical.sponsor.title.cover}
}%
\itId{sqi}{alb}{koas}{client}{li.hierarchical.sponsor.title.toc}{
\itRid{client}{li.hierarchical.sponsor.title.cover}
}%
\itId{sqi}{alb}{koas}{client}{li.hierarchical.sponsor.title.header}{
\itRid{client}{li.hierarchical.sponsor.title.cover}
}%
\itId{sqi}{alb}{koas}{actors}{People.colon}{
\itRid{actors}{People}:
}%
\itId{sqi}{alb}{koas}{actors}{Deacon.colon}{
\itRid{actors}{Deacon}:
}%
\itId{sqi}{alb}{koas}{actors}{InALowVoice.colon}{
\itRid{actors}{InALowVoice}:
}%
\itId{sqi}{alb}{koas}{actors}{Priest.colon}{
\itRid{actors}{Priest}:
}%
\itId{sqi}{alb}{koas}{actors}{Aloud.colon}{
\itRid{actors}{Aloud}:
}%
\itId{sqi}{alb}{koas}{ho.s07}{hoLI.Antiphon2.text}{
\itRid{ho.s07}{hoLI.Antiphon21.text} \itRid{ho.s07}{hoLI.Antiphon2s.text} \itRid{ho.s07}{hoLI.Antiphon22.text}
}%
\itId{sqi}{alb}{koas}{rubrical}{Aloud.colon}{
\itRid{rubrical}{Aloud}:
}%
\itId{sqi}{alb}{koas}{actors}{PriestOrDeacon.colon}{
\itRid{actors}{PriestOrDeacon}:
}%
\itId{sqi}{alb}{koas}{actors}{Chanters.colon}{
\itRid{actors}{Chanters}:
}%
\itId{sqi}{alb}{koas}{rubrical}{cl.eu.lichrysbasil.R011}{
The reading is from the Holy Gospel according to \itRid{rubrical}{name.period}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet21lash}{
\itRid{pub.priest.servicebook}{li.pet21lash.a} \color{red}[\color{black}\itRid{pub.priest.servicebook}{li.pet21lash.b} \color{red}\itRid{pub.priest.servicebook}{li.pet21lash.c} \color{black}  \itRid{pub.priest.servicebook}{li.pet21lash.d}\color{red}]\color{black}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.pet22lash}{
\itRid{pub.priest.servicebook}{li.pet22lash.a}\color{red}[\color{black}, \itRid{pub.priest.servicebook}{li.pet22lash.b} \color{red}\itRid{pub.priest.servicebook}{li.pet22lash.c} \color{black} \itRid{pub.priest.servicebook}{li.pet22lash.d}\color{red}]\color{black}.
}%
\itId{sqi}{alb}{koas}{ho.s03}{hoMA.SunPostGospel.text}{
\color{black}\itRid{ho.s03}{hoMA.SunPostGospel.text.a}\color{red}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.IfItIsSunday}{
\color{red}\itRid{pub.priest.servicebook}{li.rubric.andpsalmor1} \color{black}\itRid{pub.priest.servicebook}{li.rubric.andpsalmor2}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.IfItIsNotSunday}{
\color{red}\itRid{pub.priest.servicebook}{li.rubric.andpsalmor3} \color{black}\itRid{pub.priest.servicebook}{DefteProskinisomen0}  \color{red}\itRid{pub.priest.servicebook}{li.rubric.andpsalmor4}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.rubric.AfterPsalm50}{
\color{red}\itRid{pub.priest.servicebook}{li.rubric.forgive} \color{black}\itRid{pub.priest.servicebook}{li.forgive} \color{red}\itRid{pub.priest.servicebook}{li.rubric.orsimilar}
}%
\itId{sqi}{alb}{koas}{actors}{Chanter.colon}{
\itRid{actors}{Chanter}:
}%
\itId{sqi}{alb}{koas}{ps}{psa50.v20.v21.a.and.b}{
% \itRid{ps}{psa50.v20.text} \itRid{ps}{psa50.v21a.text} \itRid{ps}{psa50.v21b.text}
}%
\itId{sqi}{alb}{koas}{actors}{Clergy.colon}{
\itRid{actors}{Clergy}:
}%
\itId{sqi}{alb}{koas}{client}{euLI.Key1330.text}{
\itRid{client}{euLI.Key1330a.text} \itRid{client}{cl.bishop1.rank} \itRid{client}{cl.bishop1.name.p} \itRid{client}{euLI.Key1330b.text}
}%
\itId{sqi}{alb}{koas}{actors}{Reader.colon}{
\itRid{actors}{Reader}:
}%
\itId{sqi}{alb}{koas}{dismissals}{combo}{
\itRid{dismissals}{dis01} \itRid{dismissals}{dis02}  \itRid{dismissals}{dis03} \itRid{dismissals}{dis04}  \itRid{dismissals}{dis05} \itRid{dismissals}{dis06}  \itRid{dismissals}{dis07}  \itRid{dismissals}{li.dis.fathersmothers}  \itRid{dismissals}{li.dis.ofsaint}  \itRid{dismissals}{li.dis.oftemple}   \itRid{dismissals}{li.dis.chrysostom}  \itRid{dismissals}{dis09}  \itRid{dismissals}{li.dis.ofsaint}  \itRid{dismissals}{li.dis.ofday}  \itRid{dismissals}{li.dis.memory}  \itRid{dismissals}{dis10} \itRid{dismissals}{dis88}
}%


\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgycatechumens.title.toc}{
\itRid{pub.priest.servicebook}{li.liturgycatechumens.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgycatechumens.title.header}{
\itRid{pub.priest.servicebook}{li.liturgycatechumens.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.litanypeace.title.toc}{
\itRid{pub.priest.servicebook}{li.litanypeace.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.litanypeace.title.header}{
\itRid{pub.priest.servicebook}{li.litanypeace.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerantifon1.title.toc}{
\itRid{pub.priest.servicebook}{li.prayerantifon1.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerantifon1.title.header}{
\itRid{pub.priest.servicebook}{li.prayerantifon1.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.antifon1.title.toc}{
\itRid{pub.priest.servicebook}{li.antifon1.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.antifon1.title.header}{
\itRid{pub.priest.servicebook}{li.antifon1.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.smalllitany.title.toc}{
\itRid{pub.priest.servicebook}{li.smalllitany.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.smalllitany.title.header}{
\itRid{pub.priest.servicebook}{li.smalllitany.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerantifon2.title.toc}{
\itRid{pub.priest.servicebook}{li.prayerantifon2.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerantifon2.title.header}{
\itRid{pub.priest.servicebook}{li.prayerantifon2.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.antifon2.title.toc}{
\itRid{pub.priest.servicebook}{li.antifon2.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.antifon2.title.header}{
\itRid{pub.priest.servicebook}{li.antifon2.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerantifon3.title.toc}{
\itRid{pub.priest.servicebook}{li.prayerantifon3.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerantifon3.title.header}{
\itRid{pub.priest.servicebook}{li.prayerantifon3.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.antifon3.title.toc}{
\itRid{pub.priest.servicebook}{li.antifon3.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.antifon3.title.header}{
\itRid{pub.priest.servicebook}{li.antifon3.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerentrance.title.toc}{
\itRid{pub.priest.servicebook}{li.prayerentrance.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayerentrance.title.header}{
\itRid{pub.priest.servicebook}{li.prayerentrance.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.trisagionprayer.title.toc}{
\itRid{pub.priest.servicebook}{li.trisagionprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.trisagionprayer.title.header}{
\itRid{pub.priest.servicebook}{li.trisagionprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.readings.title.toc}{
\itRid{pub.priest.servicebook}{li.readings.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.readings.title.header}{
\itRid{pub.priest.servicebook}{li.readings.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.gospelprayer.title.toc}{
\itRid{pub.priest.servicebook}{li.gospelprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.gospelprayer.title.header}{
\itRid{pub.priest.servicebook}{li.gospelprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.gospel.title.toc}{
\itRid{pub.priest.servicebook}{li.gospel.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.gospel.title.header}{
\itRid{pub.priest.servicebook}{li.gospel.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.kerygma.title.toc}{
\itRid{pub.priest.servicebook}{li.kerygma.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.kerygma.title.header}{
\itRid{pub.priest.servicebook}{li.kerygma.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.greatlitany.title.toc}{
\itRid{pub.priest.servicebook}{li.greatlitany.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.greatlitany.title.header}{
\itRid{pub.priest.servicebook}{li.greatlitany.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.ekteniaprayer.title.toc}{
\itRid{pub.priest.servicebook}{li.ekteniaprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.ekteniaprayer.title.header}{
\itRid{pub.priest.servicebook}{li.ekteniaprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayercatechumens.title.toc}{
\itRid{pub.priest.servicebook}{li.prayercatechumens.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayercatechumens.title.header}{
\itRid{pub.priest.servicebook}{li.prayercatechumens.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgyfaithful.title.toc}{
\itRid{pub.priest.servicebook}{li.liturgyfaithful.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.liturgyfaithful.title.header}{
\itRid{pub.priest.servicebook}{li.liturgyfaithful.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayer1faithful.title.toc}{
\itRid{pub.priest.servicebook}{li.prayer1faithful.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayer1faithful.title.header}{
\itRid{pub.priest.servicebook}{li.prayer1faithful.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayer2faithful.title.toc}{
\itRid{pub.priest.servicebook}{li.prayer2faithful.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayer2faithful.title.header}{
\itRid{pub.priest.servicebook}{li.prayer2faithful.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.cherubic.title.header}{
\itRid{pub.priest.servicebook}{li.cherubic.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayercherubic.title.toc}{
\itRid{pub.priest.servicebook}{li.prayercherubic.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.prayercherubic.title.header}{
\itRid{pub.priest.servicebook}{li.prayercherubic.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.litanygifts.title.toc}{
\itRid{pub.priest.servicebook}{li.litanygifts.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.litanygifts.title.header}{
\itRid{pub.priest.servicebook}{li.litanygifts.title.doc}
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1202.title.toc}{
\itRid{eu.lichrysbasil}{euLI.Key1202.title.doc}
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1202.title.header}{
\itRid{eu.lichrysbasil}{euLI.Key1202.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.creed.title.toc}{
\itRid{pub.priest.servicebook}{li.creed.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.creed.title.header}{
\itRid{pub.priest.servicebook}{li.creed.title.doc}
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1300.title.toc}{
\itRid{eu.lichrysbasil}{euLI.Key1300.title.doc}
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1300.title.header}{
\itRid{eu.lichrysbasil}{euLI.Key1300.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.litanylordsprayer.title.toc}{
\itRid{pub.priest.servicebook}{li.litanylordsprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.litanylordsprayer.title.header}{
\itRid{pub.priest.servicebook}{li.litanylordsprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{titles}{KyriakiProsefchi.title.toc}{
\itRid{titles}{KyriakiProsefchi.title.doc}
}%
\itId{sqi}{alb}{koas}{titles}{KyriakiProsefchi.title.header}{
\itRid{titles}{KyriakiProsefchi.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.holycommunion.title.toc}{
\itRid{pub.priest.servicebook}{li.holycommunion.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.holycommunion.title.header}{
\itRid{pub.priest.servicebook}{li.holycommunion.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.distribution.title.toc}{
\itRid{pub.priest.servicebook}{li.distribution.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.distribution.title.header}{
\itRid{pub.priest.servicebook}{li.distribution.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.thanksdismissal.title.toc}{
\itRid{pub.priest.servicebook}{li.thanksdismissal.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.thanksdismissal.title.header}{
\itRid{pub.priest.servicebook}{li.thanksdismissal.title.doc}
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1606.title.toc}{
\itRid{eu.lichrysbasil}{euLI.Key1606.title.doc}
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1606.title.header}{
\itRid{eu.lichrysbasil}{euLI.Key1606.title.doc}
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1700.title.toc}{
\itRid{eu.lichrysbasil}{euLI.Key1700.title.doc}
}%
\itId{sqi}{alb}{koas}{eu.lichrysbasil}{euLI.Key1700.title.header}{
\itRid{eu.lichrysbasil}{euLI.Key1700.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.ambonprayer.title.toc}{
\itRid{pub.priest.servicebook}{li.ambonprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{pub.priest.servicebook}{li.ambonprayer.title.header}{
\itRid{pub.priest.servicebook}{li.ambonprayer.title.doc}
}%
\itId{sqi}{alb}{koas}{prayers}{listen.to.holy.gospel}{
\itRid{prayers}{exc17} \itRid{prayers}{exc18} \itRid{prayers}{gos02} \itRid{prayers}{pet31} 
}%